Report

### 2021-10-07 Rmd/report.Rmd
Add 25 months analysis
Update .Rprofile to include the run function
Bayesian analysis

---
title: "Report"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 5
    toc_float: true
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

# load packages
library(targets)
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(lme4)
library(broom.mixed)
library(gt)
library(patchwork)
library(htmltools)
library(wesanderson)
library(shiny)
library(tidytext)
library(here)

@@

theme_set(theme_custom()) # in utils.R
```

@@

### Counterbalancing {.tabset}

#### Stringent criteria {.tabset}

```{r child="report_05_attrition_counter_stringent.Rmd"}
```

#### Relaxed criteria {.tabset}

```{r child="report_05_attrition_counter_relaxed.Rmd"}
```

#### {-}

## 21 months-old monolinguals {.tabset}

```{r child="report_06_21-mon_stringent.Rmd"}
```

```{r child="report_06_21-mon_relaxed.Rmd"}
```

@@

```{r child="report_08_vocabulary_stringent.Rmd"}
```

@@

```{r child="report_08_vocabulary_relaxed.Rmd"}
```

>>>>

---
title: "Report"
output:
  github_document:
    pandoc_args: --webtex
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		knitr.duplicate.label = "allow",
		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

# load packages
library(targets)
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(gt)
library(patchwork)
library(wesanderson)
library(shiny)
library(tidytext)
library(brms)
library(tidyverse)
library(here)

@@

theme_set(theme_github()) # in utils.R
```

@@

@@

```{r child="report_06_vocabulary_stringent.Rmd"}
```

@@

```{r child="report_06_vocabulary_relaxed.Rmd"}
```

### 2021-10-07 Rmd/report_00_participants_relaxed.Rmd
Bayesian analysis

>>>>

```{r participants_summary_relaxed_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()

```

### 2021-10-07 Rmd/report_01_stimuli.Rmd
Bayesian analysis

frequency_compare_test %>% 
	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
	mutate(p_value = printp(p_value)) %>% 
	gt(rowname_col = "test_language") %>% 
	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
	cols_label(
		estimate = md("**Correlation**"),
		statistic = md("***t***"),
		parameter = md("***df***"),
		p_value = md("***p***"),
		conf_low = md("**CI<sub>95%<sub/>**")
	)

>>>>

frequency_compare_test %>% 
	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
	mutate(p_value = printp(p_value)) %>% 
	gt(rowname_col = "test_language") %>% 
	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
	cols_label(
		estimate = md("**Correlation**"),
		statistic = md("***t***"),
		parameter = md("***df***"),
		p_value = md("***p***"),
		conf_low = md("**CI<sub>95%<sub/>**")
	) %>% 
	as_raw_html()

### 2021-10-07 Rmd/report_04_gca_relaxed.Rmd
Bayesian analysis

### Growth curve analysis {.tabset}

@@

```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_relaxed, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_relaxed, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects
```

@@

```{r random_effects_participant_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

VarCorr(fit_relaxed)$participant %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	gt(rowname_col = "term1") %>% 
	fmt_number(columns = 2:9) %>% 
	data_color(
		columns = 2:9,
		colors = col_numeric(
			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
			domain = c(-1, 1), alpha = 0.5
		)
	)

@@

```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(valid_participant) %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) 
```

##### By vocabulary size

```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### By location

```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

augment(fit_relaxed) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

>>>>

```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit <- model_fits_relaxed$fit
```

@@

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)

draws %>% 
	mean_qi(.width = c(0.95, 0.50)) %>% 
	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
	clean_names() %>% 
	select(-c(point, interval, value_0_5)) %>% 
	gt(rowname_col = "variable") %>% 
	fmt_number(2:6) %>% 
	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		variable = md("**Predictor**"),
		value_0_95 = md("**Mean**"),
		lower_0_95 = md("**95% CrI**"),
		lower_0_5 = md("**50% CrI**")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#b9fac4")
		),
		locations = cells_body(
			columns = lower_0_95,
			rows = lower_0_95 > 0
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#b9fac4")
		),
		locations = cells_body(
			columns = lower_0_5,
			rows = lower_0_5 > 0
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#fabfb9")
		),
		locations = cells_body(
			columns = lower_0_95,
			rows = upper_0_95 < 0
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#fabfb9")
		),
		locations = cells_body(
			columns = lower_0_5,
			rows = upper_0_5 < 0
		)
	) %>% 
	as_raw_html()
```

```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}

draws %>% 
	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95, 1))))) +
	geom_vline(xintercept = 0) +
	stat_halfeye() +
	labs(x = "Value", y = "Variable", fill = "CrI") +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	theme(
		axis.title = element_blank(),
		legend.position = "top"
	)

@@

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

vcov(fit) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Mean post. correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text = element_text(hjust = 1, size = 8),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 8)
	)

@@

```{r gaze_relaxed_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant) %>% 
	count(lp)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	age_group = c("25 months"),
	trial_type = unique(gaze_relaxed$trial_type),
	time_bin_center = seq(min(gaze_relaxed$time_bin_center), max(gaze_relaxed$time_bin_center), 0.5)
)

m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
	mutate(.value = logit_to_prob(.epred))

ggplot(m, aes(time_bin_center, .value)) +
	facet_wrap(~fct_rev(lp)) +
	geom_hline(yintercept = 0.5) +
	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
				  colour = trial_type),
			  alpha = 0.15, size = 0.75) +
	stat_summary(aes(group = trial_type, colour = trial_type),
				 fun = mean, geom = "line", size = 1.25) +
	stat_summary(data = gaze_relaxed, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
							   colour = trial_type),
				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
				 position = position_dodge(width = 0.3)) +
	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 1, label = paste0("N = ", n)),
			  colour = "white", hjust = 0, size = 5) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_brewer(palette = "Set1") +
	scale_x_continuous(breaks = min(gaze_relaxed$time_bin_center):max(gaze_relaxed$time_bin_center), labels = unique(gaze_relaxed$time_bin)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 9)
	)
```
